%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Bojie Li}{}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:boj@mail.ustc.edu.cn}{boj\mbox{}@\mbox{}mail.ustc.edu.cn}\sbull
\textsmaller{+}86.15011272877\sbull
Blog: \href{https://ring0.me/}{ring0.me} (Chinese)
\\
\noindent 2nd year Ph.D. student\sbull
Joint Ph.D. program with USTC and MSRA


\spacedhrule{0.8em}{-0.8em}  % a horizontal line with some vertical spacing before and after

\roottitle{Education}

\headedsection  % sets the header for the section and includes any subsections
{\href{http://ustc.edu.cn}{University of Science and Technology of China}}
{\textsc{Hefei, Anhui, China}} {%
	\headedsubsection
	{Ph.D. in Computer Science}
	{Sept. \apo14 -- present}
	{\bodytext{Joint Ph.D. program with Microsoft Research. Advisor: \href{http://research.microsoft.com/en-us/people/kuntan/}{Kun Tan} in \href{http://research.microsoft.com/en-us/groups/wn/}{Wireless and Networking group.}}}
}

\headedsection  % sets the header for the section and includes any subsections
{\href{http://ustc.edu.cn}{University of Science and Technology of China}}
{\textsc{Hefei, Anhui, China}} {%
	\headedsubsection
	{B.S. in Computer Science (School of Gifted Young)}
	{Sept. \apo10 -- June \apo14}
	{}
}

\spacedhrule{0.5em}{-0.8em}

\roottitle{Research Interests}

\inlineheadsection{Data center networking:}{Network function virtualization.}
\inlineheadsection{Reconfigurable hardware:}{High level synthesis, Heterogeneous computing.}

\spacedhrule{1.0em}{-0.8em}

\roottitle{Publications}

\inlineheadsection
{ClickNP: Highly Flexible and High-performance Network Processing with Reconfigurable Hardware}
{\textbf{Bojie Li}, Kun Tan, Layong (Larry) Luo, Yanqing Peng, Renqian Luo, Ningyi Xu, Yongqiang Xiong and Peng Cheng \\
\textit{Proceedings of the 2016 ACM conference on SIGCOMM} (\textbf{SIGCOMM'16}) (to appear)
}

\vspace{0.5em}

\inlineheadsection
{Fast and Cautious: Leveraging Multi-path Diversity for Transport Loss Recovery in Data Centers \quad}
{Guo Chen, Yuanwei Lu, Yuan Meng, \textbf{Bojie Li}, Kun Tan, Dan Pei, Peng Cheng, Layong (Larry) Luo, Yongqiang Xiong, Xiaoliang Wang and Youjian Zhao \\
	\textit{Proceedings of the 2016 USENIX Annual Technical Conference} (\textbf{ATC'16}) (to appear)
}

\vspace{0.5em}

\spacedhrule{0.8em}{-0.8em}

\roottitle{Research Experience (selected)}

\headedsection  % sets the header for the section and includes any subsections
  {ClickNP Packet Processing Platform on FPGA}
  {\textsc{Microsoft Research Asia}} {%
  \headedsubsection
    {SIGCOMM'16, first author, instructed by \href{http://research.microsoft.com/en-us/people/kuntan/}{Kun Tan}}
    {July \apo15 -- Jan. \apo16}
    {\bodytext{
    	\begin{itemize}
    	\item The first FPGA-accelerated platform for general network functions, written completely in high-level language and achieving 40 Gbps line rate as well as $<2\mu$s latency at any packet size.
    	\item Support high throughput (25Gbps) and low latency (1$\mu$s) joint CPU-FPGA processing.
    	\item Implement the ClickNP tool-chain, which can integrate with various commercial HLS tools.
    	\item Work with two senior undergraduates to design and implement 100 elements and 5 network functions.
    	\end{itemize}
    }}
}

\headedsection  % sets the header for the section and includes any subsections
  {Fault-tolerant Switch Software Architecture}
  {\textsc{Microsoft Research Asia}} {%
	\headedsubsection
	{B.S. dissertation, instructed by \href{http://research.microsoft.com/en-us/people/kuntan/}{Kun Tan}}
	{July \apo13 -- May \apo14}
	{\bodytext{
	\begin{itemize}
		\item Design and implementation of a fault-tolerant switch software architecture allowing any component to fail or upgrade without interrupting data plane.
		\item The control plane will automatically recover within 1 minute after the failed component restarts. 
		\item Designed a daemon (SyncD) to virtualize lookup tables in programmable switching chip and resolve rule conflicts among clients.
	\end{itemize}
}}
}

\spacedhrule{0.5em}{-0.8em}

\roottitle{Engineering Experience (selected)}

\headedsection  % sets the header for the section and includes any subsections
{\href{https://git.ustclug.org/boj/freeshell}{USTC Freeshell}}
{\textsc{Univ. of Science and Tech. of China}} {%
	\headedsubsection
	{Founder and main developer}
	{Jan. \apo13 -- July \apo14}
	{\bodytext{
			\begin{itemize}
				\item Container-based IaaS service based on OpenVZ virtualization, supporting various Linux distributions.
				\item Support migration, IPv4 \& IPv6, NAPT, port mapping and HTTP(S) proxy.
				\item Support $\sim$2,000 active containers with merely 7 compute nodes, 1 storage node, 1 controller node and 2 network nodes. Optimize NFS and leverage local disk cache to improve storage efficiency.
				\item The first IaaS service in USTC, have $\sim$1,500 users. 7K lines of PHP and 1K lines of bash code.
			\end{itemize}
		}}
	}

\headedsection  % sets the header for the section and includes any subsections
{\href{https://git.ustclug.org/boj/openvpn-server/blob/master/www/index.html}{LUG VPN}}
{\textsc{Univ. of Science and Tech. of China}} {%
	\headedsubsection
	{Founder and main developer}
	{Jul. \apo13 -- July \apo14}
	{\bodytext{
			\begin{itemize}
				\item Geolocation DNS-based policy routing, load balancing and failure recovery.
				\item Access points and exit gateways in 6 ISPs, connected via GRE tunnels in star topology.
				\item $\sim$1K active users, $\sim$10K active flows and $\sim$500 Mbps traffic in peak periods.
			\end{itemize}
		}}
	}

\headedsection  % sets the header for the section and includes any subsections
{\href{https://git.ustclug.org/boj/compiler-backdoor}{Embedding Backdoor in an Open Source Compiler}}
{\textsc{Univ. of Science and Tech. of China}} {%
	\headedsubsection
	{Course project of Hacker Reverse Engineering Technology}
	{Sept. \apo12 -- Jan. \apo13}
	{\bodytext{
			\begin{itemize}
				\item Implement Ken Thompson's Turing Award lecture \textit{Reflections of Trusting Trust} on \textbf{tcc} compiler.
				\item Inserts backdoor to matches \textbf{sulogin} source code to insert login backdoor. The compiler backdoor bootstraps by matching its own source code.
			\end{itemize}
		}}
	}

\headedsection  % sets the header for the section and includes any subsections
{\href{https://git.ustclug.org/boj/rtfs}{Real-time Disk File System}}
{\textsc{Univ. of Science and Tech. of China}} {%
	\headedsubsection
	{Course project of Principles and Design of Operating Systems}
	{Mar. \apo12 -- June \apo12}
	{\bodytext{
			\begin{itemize}
			\item Improve block device scheduling algorithm and process 
				   scheduler for RTLinux-3.2 to enforce strict priority and eliminate disruptions from non-real-time tasks.
			\item Guarantee response time and throughput for real-time 
				   tasks with burst, random, streaming or pipeline I/O modes.
			\end{itemize}
		}}
	}

\spacedhrule{0.5em}{-0.8em}

\roottitle{Selected Awards}

\headedsubsection
{Microsoft Young Fellowship Scholarship}
{Aug. \apo13}
{}
\headedsubsection
{Best Creativity Award, Robogame 2011, USTC}
{Oct. \apo11}
{}
\headedsubsection
{First Prize (rank 10$^{th}$), China Mathematical Olympiad in Hebei province}
{Oct. \apo09}
{}
\headedsubsection
{Bronze Medal (rank 69$^{th}$), National Olympiad in Informatics}
{Jul. \apo09}
{}
\headedsubsection
{First Prize (rank 2$^{nd}$), National Olympiad in Informatics in Hebei province}
{Nov. \apo08}
{}

\spacedhrule{0.5em}{-0.8em}

\roottitle{Extracurricular Activities}

\headedsubsection
{Teaching Assistant, Advanced Software Engineering course, MSRA}
{Sept. \apo15 -- Jan. \apo16}
{}
\headedsubsection
{President, Linux User Group, USTC}
{May \apo12 -- May \apo13}
{}
\headedsubsection
{DevOps, GewuIT Startup Team, USTC}
{Sept. \apo12 -- May \apo13}
{}
\headedsubsection
{Founder, Technology team, Student Union, School of Gifted Young}
{Sept. \apo11 -- May \apo12}
{}

\spacedhrule{0.5em}{-0.8em}

\roottitle{Skills}

\inlineheadsection{Programming:}{C, OpenCL, Python, Verilog, Bash.}
\inlineheadsection{Web development:}{JavaScript, HTML, CSS, PHP, Node.js, Flask.}
\inlineheadsection{Linux:}{Kernel development, Network management, Server operations and monitoring.}
\inlineheadsection{Gitlab:}{\href{https://git.ustclug.org/u/boj}{https://git.ustclug.org/u/boj}}



\end{document}

＀
